Symbolic Weighted Language Models and\\ Quantitative Parsing over Infinite Alphabets

### 2021-07-10 abstract.tex
description algo search
Petits changements abstract

% !TEX root = main.tex
%
% Symbolic Weighted (SW) extension of symbolic automata...
%
We propose a framework for weighted parsing over infinite alphabets.
%
It is based on language models called Symbolic Weighted Automata (\SWA)
at the joint %intersection
between Symbolic Automata (\SA) and Weighted Automata (\WA),
as well as Transducers (\SWT) and Visibly Pushdown (\SWVPA) variants.
%
Like \SA, \SWA deal with large or infinite input alphabets,
and like \WA, they output a weight value in a semiring domain.
The transitions of \SWA are labeled by functions from an infinite alphabet into the weight domain.
This is unlike \SA whose transitions are guarded by boolean predicates
overs symbols in an infinite alphabet
and also unlike \WA whose transitions are labeled by constant weight values,
and who deal only with finite automata.
%
We present some properties of \SWA, \SWT and \SWVPA models,
%and show how they can be used
that we use to define and solve a variant of parsing
over infinite alphabets.
%
We illustrate the models with examples taken from
a motivating application, namely
a parse-based approach to automated music transcription.

>>>>

% !TEX root = main.tex
%
% Symbolic Weighted (SW) extension of symbolic automata...
%
We propose a framework for weighted parsing over infinite alphabets.
%
It is based on language models called Symbolic Weighted Automata (\SWA)
at the joint %intersection
between Symbolic Automata (\SA) and Weighted Automata (\WA),
as well as Transducers (\SWT) and Visibly Pushdown (\SWVPA) variants.
%
Like \SA, \SWA deal with large or infinite input alphabets,
and like \WA, they output a weight value in a semiring domain.
The transitions of \SWA are labeled by functions from an infinite alphabet into the weight domain.
This is unlike \SA whose transitions are guarded by Boolean predicates
overs symbols in an infinite alphabet
and also unlike \WA whose transitions are labeled by constant weight values,
and who deal only with finite automata.
%
We present some properties of \SWA, \SWT and \SWVPA models,
%and show how they can be used
that we use to define and solve a variant of parsing
over infinite alphabets.
%
We illustrate the model with a motivating application, namely
automated music transcription.
